A Pilot Multicenter Cluster Randomized Trial to Compare The Effect of Trauma Life Support Training Programs on Patient and Provider Outcomes

### 2022-09-06 pilot-publication/manuscript.Rmd
Add ClinicalTrials registration to manuscript and add section on protocol deviations

## Trial registration
This pilot study was registered with Clinical Trials Registry - India (reg. no XX) and ClinicalTrials.gov (reg. no XX).

@@

# Competing Interests
Several authors are Advanced Trauma Life Support
instructors.

@@

>>>>

## Trial registration
This pilot study was registered with ClinicalTrials.gov (reg. no NCT05417243).

@@

# Competing Interests
Several authors are Advanced Trauma Life Support or Primary Trauma Care instructors

@@

# Protocol Deviations

## Trial Registration
We intended to also register our trial with Clinical Trials Registry - India but because of time constrains we had to initiate the study before registration was finalised, and Clinical Trials Registry - India only allow prospective registration.

## Number of Participating Centres
We ended up recruiting seven centres instead of six and therefore assigned two centres each to the intervention arms and three centres to the control arm.

## Resident Participants
Emergency medicine in addition to surgery.
